### 2015-11-20 section/3_redundancy.tex
slight change to figure 3 explanation

\subsubsection{Design overview}
At high level, we will compare the computation of different iterations
from one loop instance and that of different loop instances from 
one static loop, 
and judge whether there exists redundancy.
Specifically, our design needs to answer several questions.

@@

\emph{How to lower the overhead of record-and-compare?}
We will use both static optimization and dynamic sampling
to reduce the amount of data that we need to record and compare, lowering
time and spatial overhead. Details will be presented in 
Section \ref{sec:inst} and \ref{sec:perf}.
%TODO static analysis alone is not sufficient, because some redundant is
%workload dependent

@@

For cross-loop redundancy, we need to answer similar questions.
How to judge whether two loop instances are doing redundant work ---
should they contain exactly the same number of iterations and doing exactly
the same computation in each iteration?
%Second, is a (static) loop problematic when it contains two instances that
%are redundant with each other?

>>>>

\subsubsection{Design overview}
We will compare the computation of different iterations
from one loop instance and that of different loop instances from 
one static loop,
and judge whether there is redundancy.
Specifically, several questions need to be answered.

@@

\emph{How to lower the overhead of record-and-compare?}
We will use both static optimization 
(Section \ref{sec:perf})
and dynamic sampling (Section \ref{sec:inst})
to reduce the amount of data that is recorded and compared, reducing
time and spatial overhead.
%TODO static analysis alone is not sufficient, because some redundant is
%workload dependent

@@

For cross-loop redundancy, we need to answer similar questions:
how to judge whether two loop instances are doing redundant work?
%should they contain exactly the same number of iterations and doing exactly
%the same computation in each iteration?
%Second, is a (static) loop problematic when it contains two instances that
%are redundant with each other?

### 2015-11-20 section/abstract.tex
slight change to figure 3 explanation

Writing efficient software is difficult.
Design and implementation defects can easily
lead to severe performance 
degradation. Techniques that help
diagnose performance problems are desired.
Unfortunately, existing techniques are still preliminary.
%failing to provide the desired diagnosis coverage, accuracy, and performance. 
Performance-bug detectors can identify specific type
of inefficient computation, but are not suitable for accurately diagnosing
a wide variety of real-world performance problems. 
Profilers can locate code regions that consume resources, but 
not the ones that \textit{waste} resources.
Statistical performance diagnosis can
identify loops or branches that are most correlated with a performance
symptom, but cannot decide whether and why a loop is inefficient, and
how developers might fix it.

>>>>

Writing efficient software is difficult.
Design and implementation defects can easily
cause severe performance 
degradation. 
Unfortunately, existing performance diagnosis techniques are still preliminary.
%failing to provide the desired diagnosis coverage, accuracy, and performance. 
Performance-bug detectors can identify specific type
of inefficient computation, but are not suitable for accurately diagnosing
a wide variety of real-world performance problems. 
Profilers can locate code regions that consume resources, but 
not the ones that \textit{waste} resources.
Statistical performance diagnosis can
identify loops or branches that are most correlated with a performance
symptom, but cannot decide whether and why a loop is inefficient, and
how developers might fix it.
